### 2013-05-31 doc/nips2013/introduction.tex

% Goal: parameter estimation in latent-variable models
Latent-variable log-linear models provide two complementary strengths: (i) allowing
latent representations to be automatically learned from data, and (ii)
allowing domain knowledge to be encoded in the form of features
to influence learning when appropriate.
Despite their success across many fields \cite{quattoni04crf,haghighi06prototype,liang06discrimative,kirkpatrick10painless,XXX},
learning these models remains a difficult problem due to the non-convexity of the likelihood.
Local optimization is the standard approach but is susceptible to local optima.

>>>>

% Goal: parameter estimation in latent-variable models
Latent-variable log-linear models provide two complementary strengths: (i) they allow
latent representations to be automatically learned from data, and (ii)
they allow domain knowledge to be encoded in the form of features to influence learning when appropriate.
Despite their success across many fields \cite{quattoni04crf,haghighi06prototype,liang06discrimative,kirkpatrick10painless,deselaers12latent},
learning these models remains a difficult problem due to the non-convexity of the likelihood.
Local optimization is the standard approach but is susceptible to local optima.
